% Raahul Singh Resume
% Based on Deedy Resume Template
% IMPORTANT: Compile with XeLaTeX

\documentclass[]{raahul_singh_resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

% TITLE NAME
\namesection{}{Raahul Singh}{ \urlstyle{same}
\href{mailto:raahulsingh002@gmail.com}{raahulsingh002@gmail.com} | (+91) 8279969625 | (+44) 7554539930 \\
Dehradun | London
}

% COLUMN ONE
\begin{minipage}[t]{0.33\textwidth} 

% EDUCATION
\section{Education} 

\subsection{IIIT Sri City}
\descript{BTech in Computer Science \\
and Engineering}
\location{ Cum. GPA: 8.43 / 10}
\location{August 2018 - 2022 | India}
\sectionsep

\subsection{St. Jude's School}
\location{Grad. May 2017 |  Dehradun, India}
\sectionsep

% LINKS
\section{Links} 
Website: \href{https://raahulsingh.net}{\bf raahulsingh.net} \\
Github: \href{https://github.com/Raahul-Singh}{\bf Raahul-Singh} \\
GitLab:  \href{https://gitlab.com/rasalghul2}{\bf rasalghul2} \\
LinkedIn:  \href{https://linkedin.com/in/raahulsingh42}{\bf raahulsingh42} \\
Substack:  \href{https://raahulsingh.substack.com}{\bf pathfinder} \\
Medium:  \href{https://medium.com/@_hawks_}{\bf @raahulsingh42} \\

% COURSEWORK
\section{Coursework}
\subsection{Undergraduate}
\textbullet{}Advanced Deep Learning and Neural Networks \\
\textbullet{}Artificial Intelligence and Machine Learning \\
\textbullet{}Object-Oriented Programming and Software Design \\
\textbullet{}Information Retrieval and Search Systems \\
\textbullet{}Service-Oriented Architecture and Application Development \\
\sectionsep

% SKILLS
\section{Skills}
\subsection{Programming}
Python \\
\location{Frameworks:}
PyTorch  \textbullet{} NumPy \\
Pandas  \textbullet{} PyGame  \\
SunPy \textbullet{} Dash \\
\location{Tools:}
Git  \textbullet{} Bash \\
\sectionsep

\subsection{Public Speaking}
\location{English Debate}
\textbullet{} Won First Prize in International English Debate QUANTA (2016) among speakers from 33 countries at City Montessori School, Lucknow, India \\
\textbullet{} Accumulated over 7 years of competitive debating experience in Inter-School and District-level English Debates
\sectionsep

% COLUMN TWO
\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

% EXPERIENCE
\section{Research and Engineering Experience}
\runsubsection{\lowercase{\href{https://www.phaidra.ai/}}{Phaidra}}
\descript{\\Senior AI Research Engineer}
\location{August 2020 - Present}
\vspace{\topsep}
\begin{tightemize}
        \item {Designed and implemented an end to end interactive platform for monitoring and analyzing all production models and agents for performance and biases, giving insights to Domain Experts for reliable support.}
        \item {Developed and implemented causal inference techniques to reduce bias in machine learning models, improving model fairness and reliability.}
        \item {Designed data-agnostic frameworks for incorporating domain knowledge into deep neural networks, resulting in more interpretable and physically consistent models.}
        \item {Built comprehensive ML observability pipelines and domain-specific performance monitoring systems to ensure model reliability in production.}
        \item {Engineered solutions for large-scale decision problems with complex action spaces, optimizing computational efficiency and decision quality.}
        \item {Led cross-functional collaboration between Research and Engineering teams to successfully deploy cutting-edge research into production systems.}
        \item {Achieved 15x improvement in time series prediction accuracy while reducing data requirements by 30x, successfully extending prediction horizons to 2x and 3x variables.}
\end{tightemize}
\sectionsep

\runsubsection{\lowercase{\href{https://summerofcode.withgoogle.com/archive/2020/projects/4893913812303872/}}{Google Summer Of Code '20 @ SunPy (OpenAstronomy)}}
\descript{ Student Developer }
\location{May 2020 – July 2020}
\begin{tightemize}
        \item {Developed machine learning models to forecast solar flare probabilities from Active Region data, improving prediction accuracy and reliability.}
        \item {Engineered a Search Events object for seamless querying and matching data across HFC, HEK, and HELIO astronomical databases.}
        \item {{\lowercase{\href{https://gist.github.com/Raahul-Singh/907e5af7c568a94cbb313200f034916f}}{\textbf{\emph{Link to an overview of deliverables.}}}}}
\end{tightemize}
\sectionsep

\runsubsection{Indian Institute of Technology, Roorkee}
\descript{\\ Machine Learning Intern @ The Biotech Department }
\location{May 2019 - July 2019}
\begin{tightemize}
        \item{Under the guidance of \lowercase{\href{https://www.iitr.ac.in/~BT/debsrfbt}}{\textbf{Dr. Debabrata Sircar}}, developed and implemented machine learning algorithms to predict fruit shelf-life using biochemical sensor data, achieving significant accuracy improvements.}
        \item {Conducted comprehensive analysis of fruit volatile chemicals to identify key biological parameters affecting post-harvest storage and nutritional quality.}
\end{tightemize}
\sectionsep

% % PROJECTS
% \section{PROJECTS}
% \runsubsection{\lowercase{\href{https://github.com/Raahul-Singh/games-and-ai/tree/master/tictactoe}}{Open Tic Tac Toe and Game Playing AI}}
% \descript{}
% \begin{tightemize}
%         \item {An order of \(10^{37}\) less state searches for a board size of 7 and win score of 3, for the third move of the game vs vanilla minimax. Uses limiting Field of View, spatial locality heuristic and the randomisation of search moves to play near optimally and with a near constant speed irrespective of the board size.}
% \end{tightemize}
% \sectionsep

% PATENTS
\section{PATENTS}
\runsubsection{Deterministic industrial process control}
\descript{\href{https://patents.google.com/patent/US20250021061A1}{US20250021061A1 (Jan 2025)}}
\begin{tightemize}
        \item {Co-invented and developed novel control systems for deterministic thermal constraint control, resulting in a published patent application assigned to Phaidra Inc.}
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document} 
